drivers response diversity

### 2024-07-05 drivers_response_diversity.Rmd
(ns) deleted from figure

plot_all_lms <- df_all_lms|> 
  ggplot(aes(species_richness, fit, color = category, fill = category, linetype = category)) +  
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)), color = NA, alpha = 0.3) +
  theme_classic(base_size = 16) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  scale_fill_manual(values = mycolors,
                    aesthetics = c("color", "fill"),
                    labels = c("endemic", "non-native (ns)", "non-endemic native", "translocated (ns)")) +
   scale_linetype_manual(values = c("endemic" = "solid",
                                   "non_native" = "dashed",
                                   "non_endemic_native" = "solid",
                                   "translocated" = "dashed"), labels = c("endemic", "non-native (ns)", "non-endemic native", "translocated (ns)"))

>>>>

plot_all_lms <- df_all_lms|> 
  ggplot(aes(species_richness, fit, color = category, fill = category, linetype = category)) +  
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)), color = NA, alpha = 0.3) +
  theme_classic(base_size = 16) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  scale_fill_manual(values = mycolors,
                    aesthetics = c("color", "fill"),
                    labels = c("endemic", "non-native (ns)", "non-endemic native", "translocated (ns)")) +
   scale_linetype_manual(values = c("endemic" = "solid",
                                   "non_native" = "dashed",
                                   "non_endemic_native" = "solid",
                                   "translocated" = "dashed"), labels = c("endemic", "non-native", "non-endemic native", "translocated"))
